\documentclass[11pt,a4paper]{ctexart}
\usepackage[margin=1in]{geometry}
\usepackage{booktabs}
\usepackage{longtable}
\usepackage{array}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\hypersetup{colorlinks=true,linkcolor=blue,urlcolor=blue}
\setlist[itemize]{nosep,leftmargin=1.5em}
\setlist[enumerate]{nosep,leftmargin=1.8em}

\title{Geant4-Agent Technical Details\\Geant4-Agent 技术细节报告}
\author{}
\date{2026-03-07}

\begin{document}
\maketitle

\section*{English}

\subsection*{1. Current Judgment}

The core runtime architecture is now stable enough that another P0-scale rewrite is not justified. The main chain is:

\begin{itemize}
\item LLM-first normalization
\item BERT as prior / fallback signal
\item candidate arbitration
\item validator gate
\item action-level dialogue rendering
\end{itemize}

What remains is primarily a \textbf{coverage problem}, not an architecture problem.

\subsection*{2. System Goal}

The current goal is a stable first-pass configuration workflow for:

\begin{itemize}
\item geometry
\item materials
\item source
\item physics
\item output
\end{itemize}

The design constraints are:

\begin{enumerate}
\item LLM and BERT can propose updates, but cannot commit them.
\item Session \texttt{config} is the single source of truth.
\item Every committed update must pass through Arbiter + Gate.
\item Geometry should prefer reusable operators / graph programs instead of per-scenario templates.
\item Confirmed user facts must not be overwritten unless the user explicitly authorizes it.
\end{enumerate}

\subsection*{3. Layered Architecture}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.24\linewidth} >{\raggedright\arraybackslash}p{0.68\linewidth}}
\toprule
Layer & Responsibility \\
\midrule
\texttt{builder/geometry/} & Geometry DSL, analytical feasibility checks, skeleton library, synthesis \\
\texttt{core/} & Orchestration, validation, locking, field registry, dialogue state \\
\texttt{nlu/} & LLM normalization, slot frame parsing, runtime semantic extraction, BERT prior \\
\texttt{planner/} & Clarification planning and user-facing language generation \\
\texttt{knowledge/} & Materials and schema-backed reference data \\
\texttt{ui/web/} & Local web interface and request routing \\
\texttt{scripts/} & Regression, dataset construction, training scripts \\
\bottomrule
\end{longtable}

Primary runtime entry points:

\begin{itemize}
\item \texttt{ui/web/server.py}
\item \path{core/orchestrator/session_manager.py}
\end{itemize}

\subsection*{4. Runtime Flow}

One strict turn is processed as follows:

\begin{enumerate}
\item Web UI request enters the strict API path.
\item LLM-first normalization infers intent, slot frame, and target paths.
\item Uncertainty guard prunes ungrounded fields for fuzzy / incomplete first turns.
\item Runtime semantic extraction combines LLM output, rule backfill, graph search, and BERT prior.
\item Candidates are filtered and arbitrated.
\item Validator Gate checks minimal closure and geometry-family requirements.
\item Dialogue renderer emits one of: \path{ask\_clarification}, \path{summarize\_progress}, \path{confirm\_overwrite}, \path{reject\_overwrite}, \texttt{finalize}, \path{explain\_choice}.
\end{enumerate}

\subsection*{5. Geometry Status}

\textbf{Single-solid families currently connected to the main path:}

\begin{itemize}
\item \path{single\_box}, \path{single\_tubs}, \path{single\_sphere}, \path{single\_orb}
\item \path{single\_cons}, \path{single\_trd}, \path{single\_polycone}, \path{single\_cuttubs}
\item \path{single\_trap}, \path{single\_para}, \path{single\_torus}
\item \path{single\_ellipsoid}, \path{single\_elltube}, \path{single\_polyhedra}
\end{itemize}

\textbf{Operator-graph families currently connected to the main path:}

\begin{itemize}
\item \texttt{ring}
\item \texttt{grid}
\item \texttt{nest}
\item \texttt{stack}
\item \texttt{shell}
\item \texttt{boolean}
\end{itemize}

Current assessment:

\begin{itemize}
\item The geometry system is already beyond the initial ``box / cylinder / sphere only'' stage.
\item It is good enough for a research-grade first pass.
\item It is \textbf{not} yet good enough to claim broad Geant4 engineering-geometry coverage.
\end{itemize}

\subsection*{6. Evidence From Live Regression}

\begin{table}[h]
\centering
\begin{tabular}{lcc}
\toprule
Metric & \path{v2\_12} live set & \path{v3\_24} live set \\
\midrule
Total cases & 12 & 24 \\
Pass rate & 1.0000 & 0.5000 \\
Initial alignment rate & 1.0000 & 0.9583 \\
Final alignment rate & 1.0000 & 0.9167 \\
Missing reduction rate & 1.0000 & 1.0000 \\
Confirm apply success rate & 1.0000 & 1.0000 \\
Rollback after confirm rate & 0.0000 & 0.0000 \\
Internal leak turn rate & 0.0000 & 0.0370 \\
Stale confirm case rate & 0.0000 & 0.0000 \\
\bottomrule
\end{tabular}
\end{table}

Artifacts:

\begin{itemize}
\item Stable 12-case live run: \path{docs/casebank\_regression\_2026-03-07\_145107.json}
\item Expanded 24-case live run: \path{docs/casebank\_regression\_2026-03-07\_154815.json}
\end{itemize}

\subsection*{7. Technical Interpretation of the Expanded 24-Case Run}

The 24-case run is the most important current signal.

\begin{itemize}
\item The orchestration core is stable: overwrite, confirm, reject, and closure reduction are all working.
\item The main remaining weakness is advanced geometry coverage.
\item Most failures in the 24-case run are \texttt{geometry.structure} mismatches on graph-heavy cases.
\item In other words, the system is no longer primarily failing on dialogue control. It is failing on geometry-family generalization.
\end{itemize}

Typical failure pattern:

\begin{itemize}
\item graph-intended requests such as \texttt{ring}, \texttt{grid}, \texttt{nest}, \texttt{stack}, \texttt{shell}, and \texttt{boolean}
\item incorrectly collapsed to \path{single\_box} or another single-solid family
\end{itemize}

This means the next major work item is not a rewrite of Arbiter or Gate. It is stronger graph-family routing and synthesis coverage.

\subsection*{8. Dialogue Layer Status}

The dialogue layer now uses:

\begin{itemize}
\item action-level templates
\item LLM light naturalization
\item user-visible field filtering
\end{itemize}

Internal-only paths such as:

\begin{itemize}
\item \path{geometry.graph\_program}
\item \path{geometry.chosen\_skeleton}
\item \path{geometry.root\_name}
\item \path{physics.backup\_physics\_list}
\item \path{physics.covered\_processes}
\item selection source / selection reasons metadata
\end{itemize}

are now filtered from user-facing summaries.

\subsection*{9. What Should Not Change}

The following design choices should be preserved:

\begin{enumerate}
\item no per-scenario geometry template classes
\item no direct LLM commit authority
\item no return to structure-classification centralization
\item no replacement of the strict chain with free-form LLM generation
\end{enumerate}

\subsection*{10. Immediate Next Step}

The next correct step is:

\begin{enumerate}
\item use the expanded 24-case live set as the main geometry-heavy regression target
\item analyze graph-family failure clusters
\item improve routing and synthesis for operator-graph geometry
\item only then reconsider whether BERT prior retraining is necessary
\end{enumerate}

\newpage
\section*{中文}

\subsection*{1. 当前判断}

目前核心运行架构已经基本稳定，不再需要 P0 级别的重写。当前主链已经固定为：

\begin{itemize}
\item LLM-first 标准化
\item BERT 作为先验 / 回退信号
\item 候选仲裁
\item Validator Gate 校验
\item 动作级对话渲染
\end{itemize}

当前剩余问题主要是 \textbf{覆盖度问题}，不是主架构问题。

\subsection*{2. 系统目标}

当前目标是构建一个稳定的 first-pass 配置闭环系统，覆盖：

\begin{itemize}
\item 几何
\item 材料
\item 源
\item 物理过程
\item 输出
\end{itemize}

同时满足以下硬约束：

\begin{enumerate}
\item LLM 和 BERT 只能产出候选，不能直接提交
\item 会话态 \texttt{config} 是唯一真值源
\item 所有提交都必须经过 Arbiter + Gate
\item 几何优先使用通用算子和 graph program，而不是场景模板
\item 未经用户明确同意，不覆盖已确认事实
\end{enumerate}

\subsection*{3. 分层架构}

\begin{longtable}{>{\raggedright\arraybackslash}p{0.24\linewidth} >{\raggedright\arraybackslash}p{0.68\linewidth}}
\toprule
层级 & 职责 \\
\midrule
\texttt{builder/geometry/} & 几何 DSL、理论可行性检查、skeleton 库、几何合成 \\
\texttt{core/} & 编排、验证、锁、字段注册、对话状态 \\
\texttt{nlu/} & LLM 标准化、slot frame、runtime semantic、BERT prior \\
\texttt{planner/} & 缺参追问规划、用户层自然语言生成 \\
\texttt{knowledge/} & 材料与 schema 参考数据 \\
\texttt{ui/web/} & 本地 Web 界面与请求路由 \\
\texttt{scripts/} & 回归、训练、数据集构建脚本 \\
\bottomrule
\end{longtable}

主入口：

\begin{itemize}
\item \texttt{ui/web/server.py}
\item \path{core/orchestrator/session\_manager.py}
\end{itemize}

\subsection*{4. 单轮运行链路}

严格模式下一轮处理顺序如下：

\begin{enumerate}
\item Web UI 请求进入 strict API
\item LLM-first 标准化识别意图、slot frame 与 target path
\item 不确定性门抑制 fuzzy / 缺参首轮的未锚定字段
\item runtime semantic 结合规则、graph search 与 BERT prior 形成候选
\item Arbiter 过滤与裁决候选
\item Validator Gate 检查最小闭环与几何 family 要求
\item 对话层输出动作：追问、总结、确认覆盖、拒绝覆盖、完成、解释选择
\end{enumerate}

\subsection*{5. 几何现状}

\textbf{已接入主链的单体 family：}

\begin{itemize}
\item \path{single\_box}、\path{single\_tubs}、\path{single\_sphere}、\path{single\_orb}
\item \path{single\_cons}、\path{single\_trd}、\path{single\_polycone}、\path{single\_cuttubs}
\item \path{single\_trap}、\path{single\_para}、\path{single\_torus}
\item \path{single\_ellipsoid}、\path{single\_elltube}、\path{single\_polyhedra}
\end{itemize}

\textbf{已接入主链的 graph family：}

\begin{itemize}
\item \texttt{ring}
\item \texttt{grid}
\item \texttt{nest}
\item \texttt{stack}
\item \texttt{shell}
\item \texttt{boolean}
\end{itemize}

当前判断：

\begin{itemize}
\item geometry 已明显超出最早三类基本体阶段
\item 研究原型级 first pass 已经够用
\item 但仍不足以宣称覆盖大多数 Geant4 工程几何
\end{itemize}

\subsection*{6. Live 回归证据}

\begin{table}[h]
\centering
\begin{tabular}{lcc}
\toprule
指标 & \path{v2\_12} live 集 & \path{v3\_24} live 集 \\
\midrule
总案例数 & 12 & 24 \\
通过率 & 1.0000 & 0.5000 \\
初始对齐率 & 1.0000 & 0.9583 \\
最终对齐率 & 1.0000 & 0.9167 \\
缺参减少率 & 1.0000 & 1.0000 \\
确认应用成功率 & 1.0000 & 1.0000 \\
确认后回滚率 & 0.0000 & 0.0000 \\
内部字段泄漏率 & 0.0000 & 0.0370 \\
陈旧确认状态率 & 0.0000 & 0.0000 \\
\bottomrule
\end{tabular}
\end{table}

对应结果文件：

\begin{itemize}
\item 稳定 12-case 集：\path{docs/casebank\_regression\_2026-03-07\_145107.json}
\item 扩展 24-case 集：\path{docs/casebank\_regression\_2026-03-07\_154815.json}
\end{itemize}

\subsection*{7. 对 24-case 扩展集的技术解释}

24-case 回归是当前最关键的信号。

\begin{itemize}
\item 编排核心是稳定的：overwrite、confirm、reject、缺参收敛都正常
\item 当前主要薄弱点是高级几何覆盖
\item 24-case 中大多数失败集中在 graph-heavy 场景的 \texttt{geometry.structure} 错判
\item 也就是说，当前系统已经不再主要失败在“对话控制”，而是失败在“几何 family 泛化”
\end{itemize}

典型失败模式是：

\begin{itemize}
\item 本应识别为 \texttt{ring}、\texttt{grid}、\texttt{nest}、\texttt{stack}、\texttt{shell}、\texttt{boolean}
\item 最终却被压缩成 \path{single\_box} 或其他单体 family
\end{itemize}

这说明下一阶段重点不是重写 Arbiter 或 Gate，而是增强 operator-graph 几何的路由与合成能力。

\subsection*{8. 对话层现状}

当前对话层采用：

\begin{itemize}
\item 动作级模板
\item LLM 轻度自然化
\item 用户可见字段过滤
\end{itemize}

以下内部字段目前已从用户层摘要中过滤：

\begin{itemize}
\item \path{geometry.graph\_program}
\item \path{geometry.chosen\_skeleton}
\item \path{geometry.root\_name}
\item \path{physics.backup\_physics\_list}
\item \path{physics.covered\_processes}
\item 各类 \path{selection\_source} / \path{selection\_reasons}
\end{itemize}

\subsection*{9. 不应再改变的设计}

以下设计不建议再回退：

\begin{enumerate}
\item 不引入 per-scenario geometry template class
\item 不给 LLM 直接提交权
\item 不回到结构分类中心化
\item 不把 strict 主链替换成自由生成
\end{enumerate}

\subsection*{10. 下一步}

当前正确的下一步是：

\begin{enumerate}
\item 用扩展 24-case live 集继续压 geometry-heavy 场景
\item 聚焦分析 graph family 失败簇
\item 补强 operator-graph 的路由和合成
\item 在此之后再决定是否需要重训 BERT prior
\end{enumerate}

\end{document}
